Model Search in Relational Domains

### 2016-10-23 example.tex
typo

BMC converts the program into a bit-vector equation and passes that to a
CDCL-based SAT solver.  We will contast the analysis performed by CDCL with
that of ACDCL.  The right-hand side of Figure~\ref{fig:example} illustrates
an analysis using ACDCL with the octagon domain (top) and the interval
domain (bottom). The analysis associates an abstract element with each
control location.  The octagons deduced by ACDCL are sufficient
to prove safety without any decision or clause learning, as in the case of
Astr{\'e}e.

@@

Table~\ref{solver} compares statistics for the MiniSAT~\cite{minisat}
solver for $N=46000$ for the analysis using BMC, and the analysis using
ACDCL with the interval and octagon domains.  Compared to the propositional
SAT solver, there is a significant reduction in the number of decisions,
propagations, learnt clauses and restarts.  Compared to abstract
interpretation, ACDCL does not require external hints to prove the program,
thus automatically performing program and property-driven trace partitioning
to generate proofs using heuristic decisions and clause learning.

>>>>

BMC converts the program into a bit-vector equation and passes that to a
CDCL-based SAT solver.  We will contrast the analysis performed by CDCL with
that of ACDCL.  The right-hand side of Figure~\ref{fig:example} illustrates
an analysis using ACDCL with the octagon domain (top) and the interval
domain (bottom). The analysis associates an abstract element with each
control location.  The octagons deduced by ACDCL are sufficient
to prove safety without any decision or clause learning, as in the case of
Astr{\'e}e.

@@

Table~\ref{solver} compares statistics for the MiniSat~\cite{minisat}
solver for $N=46000$ for the analysis using BMC, and the analysis using
ACDCL with the interval and octagon domains.  Compared to the propositional
SAT solver, there is a significant reduction in the number of decisions,
propagations, learnt clauses and restarts.  Compared to abstract
interpretation, ACDCL does not require external hints to prove the program,
thus automatically performing program and property-driven trace partitioning
to generate proofs using heuristic decisions and clause learning.
